DNA Methylation Analysis

### 2023-02-16 DNA-methylation.Rmd
added trim code

---
title: 'DNA Methylation Analysis'
subtitle: '*Steven Roberts*, and *Sam White* '
bibliography: DNA-Methylation.bib
---

@@

@@

>>>>

---
title: 'DNA Methylation Analysis'
subtitle: '*Steven Roberts* and *Sam White* '
bibliography: DNA-Methylation.bib
---

@@

```
/gscratch/srlab/programs/TrimGalore-0.4.5/trim_galore \
--output_dir /gscratch/scrubbed/strigg/analyses/20200311/WGBS_MBD \
--paired \
--fastqc_args \
--outdir /gscratch/scrubbed/strigg/analyses/20200311/WGBS_MBD/FASTQC \
--threads 28 \
--illumina \
--clip_R1 10 \
--clip_R2 10 \
--three_prime_clip_R1 10 \
--three_prime_clip_R2 10 \
--path_to_cutadapt /gscratch/srlab/programs/miniconda3/bin/cutadapt \
/gscratch/scrubbed/sr320/froger-raw/00_fastq/Meth17_R1_001.fastq.gz \
```

@@

# Read Alignment
